---
title: "gantt"
subtitle: "in development in targets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gantt}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

knitr::opts_knit$set(root.dir = here::here())

```

```{r setup, message=FALSE}
library(pandan)
library(targets)
library(gt)
library(tidyverse)

```

## Objective

A Gantt chart of my current progress with current projects with the features:

- [ ] Subprojects whose start times take into account dependencies.
- [ ] Scrapes from gs.
- [ ] Easy entry gs.
- [ ] Shaded progress bar of total project.
- [ ] Beta distribution estimated time based on Optimistic, Normal, and Pessimistic 
predictions.

## Development status

```{r fig.width=10, fig.align='center', echo=FALSE, message=FALSE,warning=FALSE,output=FALSE}
tar_glimpse()
```


## Dependencies

```{r}
# dev dataset
tar_load(obs_proj)

obs_proj %>% gt()
```

Based on these data, when _should_ the start and end points be?

Component `a_1` is not dependent on anything, and it is a top-level project, so its start and end times should span at its instantiated endpoint. 

```{r}
obs_proj %>% 
  filter(component == "a_1") %>% 
  select(project, start_inst, end_inst) %>% 
  gt()

```

Component `a_1.1` is dependent on `a_1.2.1`. So, the start point needs to be endpoint of `a_1.2.1`.

```{r}
obs_proj %>% 
  filter(component == "a_1.1") %>%
  pull(pred)

```

